DeepAutoTrack (DAC): Car Trajectory Prediction for Autonomous Driving

### 2017-11-13 paper/cvpr2018/cvpr2018_draft.tex

\documentclass[10pt,twocolumn,letterpaper]{article}
 \pdfoutput=1
\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}

%\usepackage{subcaption}

%\usepackage{slashbox}
\usepackage{color}
\usepackage[english]{babel}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

@@

@@

%%% TY: write related work for object detection, segmentation, instance segmentation
\textbf{\emph{1. Object detection, segmentation, instance segmentation}}
%%% DW: write related work for visual tracking
%%% DW: write related dataset for autonoumous driving

@@

Recently, RNN(recurrent network) and its variant LSTM(long short-term memory) have been successfully used in autonomous driving, due to its advantages for modeling sequential data in vision problems. Most of these works exploit LSTM as component of an end-to-end driving model. ~\cite{xu2017end} used the combination of a fully-convolutional network and an LSTM to learn from large-scale vehicle action data, to predict future egomotion including multi-modal discrete and continuous driving behaviors. ~\cite{kim2017interpretable} used a LSTM network to predict the inverse turning radius and generate a heat map of attention at each timestep conditioned on the previous hidden states and a current convolutional feature cube. ~\cite{duself} used 3D convolutional layers to extract visual features, then fed them into LSTM layers to capture the sequential relation. In addition to using deep features, ~\cite{koutnik2013evolving} trained a large recurrent neural network using a reinforcement learning approach to map images directly to steering angles, with the purpose to keep the car on track.

>>>>

\documentclass[10pt,twocolumn,letterpaper]{article}
 \pdfoutput=1
\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
%\usepackage{subcaption}
%\usepackage{slashbox}
\usepackage{color}
\usepackage[english]{babel}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

@@

\begin{figure}

\includegraphics[width=8.8cm]{pool_figure}
\caption{pool figure}
\label{figure10}
\end{figure}

@@

%%% TY: write related work for object detection, segmentation, instance segmentation
\textbf{\emph{1. Object detection, segmentation, instance segmentation}}
%%% DW: write related work for visual tracking
%%% DW: write related dataset for autonoumous driving
Object detection is an important component in our system. Before the resurgence of convolutional neural network (CNN), Deformable Part Model (DPM) \cite{felzenszwalb2008discriminatively} and Selective Search \cite{Uijlings2013Selective} are the trend of this field. However, after the proposal of R-CNN \cite{girshick2014rich}, which combines Selective Search and deep learning features to detect objects, the architecture of CNN has attracted more attention. At the beginning, R-CNN is a step-by-step and inefficient method. Then, SPPNet \cite{He2015Spatial} exploits a spatial pyramid pooling layer to extract multi-scale deep features and Fast R-CNN \cite{Girshick2015Fast} introduces the multi-task learning to fine-tune all layers in their network. At last, Faster R-CNN \cite{Ren2015Faster} proposes a region proposal network (RPN) and integrates RPN and Fast R-CNN to build a end-to-end architecture. Meanwhile, SSD \cite{liu2016ssd} uses a series of boxes and directly gives the probability for each object class. In addition, YOLO \cite{redmon2016you} proposes a fast object detection method, which divides the input image into grids, then predicts object positions and confidences for each category in each grid.

At the field of semantic segmentation, many methods with CNN also bring a dramatic improvement. FCN \cite{long2015fully} firstly transfers the fully-connected layers into convolution layers, which turns segmentation task into pixel-wise classification task. Deeplab \cite{chen2016deeplab} considers the limitation of receptive field of CNN, and then proposes a dilated convolution layer to solve this problem. DRN \cite{yu2017dilated} further proposes a semantic network by integrating residual structure and dilated convolution. With the modification of neural network, conditional random field (CRF) is employed into refining the output of network in \cite{chen2016deeplab}. After that, CRF is merged into neural network to become an end-to-end architecture \cite{liu2015semantic,zheng2015conditional,arnab2016higher}

@@
